Apache Flink\texttrademark: Stream and Batch Processing in a Single Engine

### 2016-05-25 paper.tex
symbols for authors

\author{Paris Carbone\textsuperscript{1} \\ Asterios Katsifodimos\textsuperscript{3} \\\\ \small{ \textsf{\small \textsuperscript{1}KTH \& SICS Sweden}} \\ \small \href{parisc,haridi@kth.se}{parisc,haridi@kth.se}
\and Stefan Ewen\textsuperscript{2} \\ Volker Markl\textsuperscript{3} \\\\ \small \textsf{\textsuperscript{2}Data Artisans GmbH} \\ \small \href{first@data-artisans.de}{first@data-artisans.de}
\and Seif Haridi\textsuperscript{1} \\ Kostas Tzoumas\textsuperscript{2} \\\\ \small \textsf{\textsuperscript{3}TU Berlin} \\ \small \href{fist.last@tu-berlin.de}{first.last@tu-berlin.de}
%
\vspace{-5mm}
}

@@

\begin{abstract}
Apache Flink \footnote{The authors of this paper make no claim in being the sole inventors or implementers of the ideas behind Apache Flink that are presented, but rather a group of people that attempt to accurately document these concepts and their significance in writing. For a complete list see \autoref{sec:acknowledgements}} is an open-source system for processing streaming and batch data. Flink is built on the philosophy that many classes of data processing applications, including real-time analytics, continuous data pipelines, historic data processing (batch), and iterative algorithms (machine learning, graph analysis) can be expressed and executed as pipelined fault-tolerant dataflows. In this paper, we present Flink's architecture and expand on how a (seemingly diverse) set of use cases can be unified under the same execution model.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
Data-stream processing (e.g, as exemplified by Complex Event Processing systems) and static (batch) data processing (e.g., as exemplified by MPP databases and Hadoop ) were traditionally considered as two very different types of applications. They were programmed using different programming models and APIs, and were executed by different systems (e.g., dedicated streaming systems such as  Apache Storm, IBM Infosphere Streams, Microsoft StreamInsight, or Streambase versus relational databases or execution engines for Hadoop, including Apache Spark, and Apache Drill). Traditionally, batch data analysis made up for the lion's share of the use cases, data sizes, and market, while streaming data analysis mostly served specialized applications.

>>>>

\author{Paris Carbone\textsuperscript{$\dagger$} \\ Asterios Katsifodimos\textsuperscript{*} \\\\ \small{ \textsf{\small \textsuperscript{$\dagger$}KTH \& SICS Sweden}} \\ \small \href{parisc,haridi@kth.se}{parisc,haridi@kth.se}
\and Stephan Ewen\textsuperscript{$\ddagger$} \\ Volker Markl\textsuperscript{*} \\\\ \small \textsf{\textsuperscript{$\ddagger$}Data Artisans GmbH} \\ \small \href{first@data-artisans.de}{first@data-artisans.de}
\and Seif Haridi\textsuperscript{$\dagger$} \\ Kostas Tzoumas\textsuperscript{$\ddagger$} \\\\ \small \textsf{\textsuperscript{*}TU Berlin} \\ \small \href{fist.last@tu-berlin.de}{first.last@tu-berlin.de}
%
\vspace{-5mm}
}

@@

\begin{abstract}
Apache Flink \footnote{The authors of this paper make no claim in being the sole inventors or implementers of the ideas behind Apache Flink, but rather a group of people that attempt to accurately document these concepts and their significance. Consult \autoref{sec:acknowledgements} for acknowledgements.} is an open-source system for processing streaming and batch data. Flink is built on the philosophy that many classes of data processing applications, including real-time analytics, continuous data pipelines, historic data processing (batch), and iterative algorithms (machine learning, graph analysis) can be expressed and executed as pipelined fault-tolerant dataflows. In this paper, we present Flink's architecture and expand on how a (seemingly diverse) set of use cases can be unified under the same execution model.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
Data-stream processing (e.g, as exemplified by Complex Event Processing systems) and static (batch) data processing (e.g., as exemplified by MPP databases and Hadoop) were traditionally considered as two very different types of applications. They were programmed using different programming models and APIs, and were executed by different systems (e.g., dedicated streaming systems such as  Apache Storm, IBM Infosphere Streams, Microsoft StreamInsight, or Streambase versus relational databases or execution engines for Hadoop, including Apache Spark, and Apache Drill). Traditionally, batch data analysis made up for the lion's share of the use cases, data sizes, and market, while streaming data analysis mostly served specialized applications.
